Fitness effects of mutations to SARS-CoV-2 proteins

### 2023-01-27 paper/paper.tex
elaborate on Mpro / yeast DMS diffs

The sequence-based estimates for Mpro also correlate with the deep mutational scans for that protein, although in this case the two experiments correlate substantially better with each other than with our estimates (Figure~\ref{fig:dms}B).
Because both Mpro experiments use a similar methodology~\citep{flynn2022,iketani2022functional} it is possible that the higher correlation of the experiments with each other versus the sequence-based estimates reflects shared artifacts of the yeast-based assay across experiments.
For instance, a stop codon at Q306 is well tolerated in both deep mutational scans but extremely disfavorable in our sequence-based estimates, and such a mutation would be highly deleterious to actual virus as it would truncate the polyprotein.
Similarly, K61N is well tolerated in the deep mutational scanning but extremely disfavorable in our estimates, possibly because in the full viral polyprotein this residue mediates important interactions between Mpro and nsp7-10~\citep{yadav2022biochemical}

>>>>

The sequence-based estimates for Mpro also correlate with the deep mutational scans for that protein, although in this case the two experiments correlate substantially better with each other than with our estimates (Figure~\ref{fig:dms}B).
Because both Mpro experiments use a similar yeast-based methodology~\citep{flynn2022,iketani2022functional} it is possible that the higher correlation of the experiments with each other than the sequence-based estimates reflects shared artifacts of the yeast experiments.
In particular, some Mpro mutations estimated to have deleterious effects in natural sequences are well tolerated in the yeast experiments.
This difference could arise if the yeast experiments only capture some of the constraints on Mpro in the context of actual virus.
For instance, a stop codon at Q306 is well tolerated in both deep mutational scans but extremely disfavorable in our sequence-based estimates, and would be highly deleterious to actual virus as it would truncate the polyprotein.
Similarly, K61N is well tolerated in the deep mutational scans but extremely disfavorable in our estimates, possibly because in the full viral polyprotein this residue mediates important interactions between Mpro and nsp7-10~\citep{yadav2022biochemical}
